25 years of Social Work Research

### 2015-02-24 dataCleaning.Rmd
Code correction for Arete
Code clean up on journal titles in pre-processing

  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
  #from duplicate entries
  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
  combined.DF<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]

@@

full.df$record <- ifelse(full.df$record == 
    "The British Journal Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Aretê^",                                   #Spelling difference
      "Arete",
              full.df$record)

@@

full.df$record <- ifelse(full.df$record ==
    "INDIAN JOURNAL OF SOCIAL WORK",
        "Indian Journal of Social Work",
                      full.df$record)

full.df$record <- ifelse(full.df$record ==
    "The Indian Journal of Social Work",
        "Indian Journal of Social Work",
                            full.df$record)

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "Arete: Revista de Filosofia")

@@

>>>>

  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
  #from duplicate entries
  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
  full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]

@@

full.df$record <- ifelse(full.df$record == 
    "The British Journal of Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Revista de Asistenta Sociala (Social Work Review)",
        "Social Work Review",
                        full.df$record)

full.df$record <- gsub("Arete", "xxx", full.df$record)
full.df$record <- gsub("Aret.{1,3}", "Arete", full.df$record)
full.df$record <- gsub("xxx", "Arete", full.df$record) 
                                      #Replaces special character       
                                      #in Arete and preserves other formatting

@@

full.df$record <- ifelse(full.df$record ==
    "INDIAN JOURNAL OF SOCIAL WORK",                    #Spelling difference
        "Indian Journal of Social Work",
                      full.df$record)

full.df$record <- ifelse(full.df$record ==
    "The Indian Journal of Social Work",              #Spelling difference
        "Indian Journal of Social Work",
                            full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Asia Pacific Journal of Social Work",              #Spelling difference
        "Asia Pacific Journal of Social Work and Development",
                            full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Social Work & Society",                           #Spelling difference
        "Social Work and Society",
                            full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Journal of Social Work in Disability & Rehabilitation",
        "Journal of Social Work in Disability and Rehabilitation", 
                            full.df$record)           #Spelling difference

full.df$record <- ifelse(full.df$record ==
    "Hong Kong Journal of Social Work",
        "The Hong Kong Journal of Social Work", 
                            full.df$record)           #Spelling difference

full.df$record <- ifelse(full.df$record ==
    "The Journal of Baccalaureate Social Work",
        "Journal of Baccalaureate Social Work", 
                            full.df$record)           #Spelling difference

full.df$record <- ifelse(full.df$record ==
    "Journal of Practice Teaching in Health and Social Work",
        "Journal of Practice Teaching in Social Work and Health", 
                            full.df$record)           #Spelling difference

full.df$record <- ifelse(full.df$record ==
    "Professional Development: The International Journal of Continuing Social Work Education",
        "Professional Development", 
                            full.df$record)           #Spelling difference

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "Professional Development in Education",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "Arete: Revista de Filosofia",
    "Arete Revista de Filosofia")

@@

full.df$record <- ifelse(full.df$record ==
        "Journal of Practice Teaching in Social Work and Practice", #Old title
        "Journal of Practice Teaching in Social Work and Health",   #New title
                    full.df$record)
